Accessing biological data with semantic web technologies

### 2013-12-26 article.tex
Fixed the affiliation data layout

\title{Accessing biological data with semantic web technologies}
\author{Egon L.\ Willighagen$^1,2$}
\begin{document}

@@

\noindent
$^1$ Department of Bioinformatics - BiGCaT, NUTRIM, Maastricht University, Maastricht, The Netherlands
$^2$ Department of Molecular Toxicology, IMM, Karolinska Institutet, Stockholm, Sweden

@@

Taking advantage of

>>>>

\title{Accessing biological data with semantic web technologies}
\author{Egon L.\ Willighagen$^{1,2}$}
\begin{document}

@@

\noindent
$^1$ Department of Bioinformatics - BiGCaT, NUTRIM, Maastricht University, Maastricht, The Netherlands \\
$^2$ Department of Molecular Toxicology, IMM, Karolinska Institutet, Stockholm, Sweden

@@

Taking advantage of ...
